Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-03 ind_files/03_field_eqns.tex
Minor phrasing changes

This constitutes the `mesoscopic' description of our process. We can once again appeal to the link between Fokker-Planck equations and Langevins \citep{lafuerza_role_2016} to say that \eqref{functional_FPE} corresponds to the Langevin equation:
\begin{equation}
\label{functional_langevin}
    \frac{\partial \phi}{\partial t}(x,t) = \mathcal{A}^{-}(x|\phi) + \frac{1}{\sqrt{K}}\eta(x,t)
\end{equation}
where $\eta(x,t)$  is the `Gaussian spacetime white noise' with zero mean and autocovariance function
\begin{equation*}
    \mathbb{E}[\eta(x,t)\eta(x',t')] = \sqrt{\mathcal{A}^{+}(x|\phi)\mathcal{A}^{+}(x'|\phi)}\delta(x-x')\delta(t-t')
\end{equation*}
If one wishes to be mathematically careful, the connection between \eqref{functional_FPE} and \eqref{functional_langevin} becomes somewhat tenuous. In particular, while the equivalence between Fokker-Planck equations and SDEs (Langevin equations) for finite-dimensional stochastic processes is part of the standard mathematical canon, the corresponding equivalence is much less well understood for the infinite-dimensional function-valued processes that we are dealing with, and the interpretation of any formal `Langevin equation' (corresponding now to a stochastic partial differential equation, or SPDE) that we write down is unclear for general measure spaces - We may need $\mathcal{M}_K$ to have a considerable amount of structure (Ex: Seperable Hilbert space) for things to work out \citep{da_prato_stochastic_2014,balan_gentle_2018}, and I do not know whether our domain is nice enough. For example, it is not immediately clear what conditions on $\mathcal{A}^{\pm}(x | \phi)$ for \eqref{functional_langevin} to even admit a solution. Nevertheless, we can recover some well-known deterministic equations from equation \eqref{deterministic_traj}, and under certain assumptions, equations like \eqref{nD_eqn_for_frequencies} have been proved to exist.

>>>>

This constitutes the `mesoscopic' description of our process. We can once again appeal to the link between Fokker-Planck equations and Langevins \citep{lafuerza_role_2016} to say that \eqref{functional_FPE} corresponds to the Langevin equation:
\begin{equation}
\label{functional_langevin}
    \frac{\partial \phi}{\partial t}(x,t) = \mathcal{A}^{-}(x|\phi) + \frac{1}{\sqrt{K}}\eta(x,t)
\end{equation}
where $\eta(x,t)$  is the `Gaussian spacetime white noise' with zero mean and autocovariance function
\begin{equation*}
    \mathbb{E}[\eta(x,t)\eta(x',t')] = \sqrt{\mathcal{A}^{+}(x|\phi)\mathcal{A}^{+}(x'|\phi)}\delta(x-x')\delta(t-t')
\end{equation*}
If one wishes to be mathematically careful, the connection between \eqref{functional_FPE} and \eqref{functional_langevin} becomes somewhat tenuous. In particular, while the equivalence between Fokker-Planck equations and SDEs (Langevin equations) for finite-dimensional stochastic processes is part of the standard mathematical canon, the corresponding equivalence is much less well understood for the infinite-dimensional function-valued processes that we are dealing with, and the interpretation of any formal `Langevin equation' (corresponding now to a stochastic partial differential equation, or SPDE) that we write down is unclear for general measure spaces - We may need $\mathcal{M}_K$ to have a considerable amount of structure (Ex: Seperable Hilbert space) for things to work out \citep{da_prato_stochastic_2014,balan_gentle_2018}, and I do not know whether our domain is nice enough. For example, it is not immediately clear what conditions on $\mathcal{A}^{\pm}(x | \phi)$ are needed for \eqref{functional_langevin} to even admit a solution. Nevertheless, we can recover some well-known deterministic equations from equation \eqref{deterministic_traj}, and under certain assumptions, equations like \eqref{nD_eqn_for_frequencies} have been proved to exist.
